Drawing Math

### 2022-05-13 paper/Paper.tex
CLEAN COMPLEX

\subsection{Algorithm complexity}
The algorithm we provide in equation \eqref{eq:singleDelta0} runs in time exponential 
in the size of the input assuming the Word RAM model. 
The period for the rational generated from rational parameter $j$, $1 \leq \rationalPeriod \leq d^j$. Then,
the period over all rationals generated from parameters is at most 
$$
  \lcm{j \in [k]} \rationalPeriod \leq \prod_{j \in [k]} \rationalPeriod \leq \left(\max_{j \in [k]} \; d^j \right)^k.
$$
Then, 
$0 \leq \totalPeriod \leq \rationalPeriodTotal \cdot \lcm{j \in [k]} b^j \leq \rationalPeriodTotal \left(\max_{j \in [k]} b^j\right)^k$.
And because evaluating the product in \eqref{eq:singleDelta0} takes $O(k)$ time,
we have that the time for \eqref{eq:singleDelta0} is at most
$$
  O\left(\left[\max_{j \in [k]} \; (b^j d^j)\right]^k \right).
$$

Then, note that computing the period of rational numbers via known classical methods takes 
exponential time in the number of digits of the denominator. So, computing
$\rationalPeriod$ takes $O(d^j)$ time. Then, computing the $\digSumPeriodic$
can take $O(d^j)$ time. 
We can thus see that period finding takes at most
$$
O\left(k \max_{j \in [k]} d^j \right)
$$
time.

Because \eqref{eq:singleDelta0} must be computed for each dimension, the algorithm
runs in 
$$
  O\left(k \max_{j \in [k]} d^j \right) + 
  O\left(\max_{j \in [k]} \; D (b^j d^j)^k \right) = 
  O\left(\max_{j \in [k]} \; D (b^j d^j)^k \right)
$$
time.
Note that $b^j, d^j$ are also exponential in the size of the input. 
We can thus see that our running time is quite atrocious (its worse than exponential).
Moreover, the algorithm does not produce a proof, verifiable in polytime, for closure 
or lack there of. Thus, our algorithm is in neither NP or coNP.

>>>>

\subsection{Algorithm complexity}
The algorithm we provide in equation \eqref{eq:singleDelta0} runs in worse than exponential time
in the size of the input assuming the Word RAM model. 
The period for the rational generated from rational parameter $j$, $1 \leq \rationalPeriod \leq d^j$. Then,
the period over all rationals generated from parameters is at most 
$$
  \lcm{j \in [k]} \rationalPeriod \leq \prod_{j \in [k]} \rationalPeriod \leq \left(\max_{j \in [k]} \; d^j \right)^k.
$$
Then, 
$0 \leq \totalPeriod \leq \rationalPeriodTotal \cdot \lcm{j \in [k]} b^j \leq \rationalPeriodTotal \left(\max_{j \in [k]} b^j\right)^k$.
And because evaluating the product in \eqref{eq:singleDelta0} takes $O(k)$ time,
we have that the time for \eqref{eq:singleDelta0} is at most
$$
  O\left(\left[\max_{j \in [k]} \; (b^j d^j)\right]^k \right).
$$

Then, note that computing the period of rational numbers via known classical methods takes 
exponential time in the number of digits of the denominator. So, computing
$\rationalPeriod$ takes $\widetilde{O}(d^j)$ time. Then, computing the $\digSumPeriodic$
can take $O(d^j)$ time. 
We can thus see that period finding takes at most
$$
\widetilde{O}\left(k \max_{j \in [k]} d^j \right)
$$
time.

Because \eqref{eq:singleDelta0} must be computed for each dimension, the algorithm
runs in 
$$
  \widetilde{O}\left(k \max_{j \in [k]} d^j \right) + 
  O\left(\max_{j \in [k]} \; D (b^j d^j)^k \right) = 
  \widetilde{O}\left(\max_{j \in [k]} \; D (b^j d^j)^k \right)
$$
time.
Note that $b^j, d^j$ are also exponential in the size of the input. 
We can thus see that our running time is quite atrocious (its worse than exponential).
Moreover, the algorithm does not produce a proof, verifiable in polytime, for closure 
or lack there of. Thus, our algorithm is in neither NP or coNP.
